### 2016-02-04 inputs/materials_and_methods.tex
phrasing

\subsection{Software}
\label{sec:software}
Data handling, editing and preparation, summary of results and plots were all performed using the open-source environment for statistical programming R \cite{r_core_team_r:_2014}. All imputation methods except Beagle and FILLIN were implemented in R: MNI directly in base R; KNNI using the function \emph{knncatimpute()} from the Scrime package \cite{schwender_scrime:_2013}; SVDI with the R package ``bcv'' \cite{perry_bcv:_2009}; RFI using the ``MissForest'' \cite{stekhoven_missforestnon-parametric_2012} R package (with parameters: ntree=100, maxiter=10, parallelize='variables'). The ``Beagle'' localized haplotype clustering imputation method was implemented with the Beagle software version 3.3.2 \cite{browning_rapid_2007}. The FILLIN algorithm is implemented using the Tassel CLI plugin \emph{-FILLINFindHaplotypesPlugin} followed by \emph{-FILLINImputationPlugin}. The latter allowed accuracy measurements through \emph{-accuracy} and \emph{-propSitesMask} options.\\
The Bowtie 2 tool \cite{langmead_fast_2012} was used to query the consensus sequence of each alfalfa tag pair containing a SNP against the \emph{M. truncatula} reference genome Version 4.0 using the \emph{-verysensitivelocal} preset. The BWA alignment tool \cite{li2009fast} was used to align rice tags on Rice Genome Annotation Project Release 7.

>>>>

\subsection{Software}
\label{sec:software}
Data handling, editing and preparation, summary of results and plots were all performed using the open-source environment for statistical programming R \cite{r_core_team_r:_2014}. All imputation methods except Beagle and FILLIN were implemented in R: MNI directly in base R; KNNI using the function \emph{knncatimpute()} from the Scrime package \cite{schwender_scrime:_2013}; SVDI with the R package ``bcv'' \cite{perry_bcv:_2009}; RFI using the ``MissForest'' \cite{stekhoven_missforestnon-parametric_2012} R package (with parameters: ntree=100, maxiter=10, parallelize='variables'). The ``Beagle'' localized haplotype clustering imputation method was implemented with the Beagle software version 3.3.2 \cite{browning_rapid_2007}. The FILLIN algorithm \cite{swarts_novel_2014} is implemented using the Tassel CLI plugin \emph{FILLINFindHaplotypesPlugin} followed by \emph{FILLINImputationPlugin}. The latter allowed accuracy measurements through \emph{-accuracy} and \emph{-propSitesMask} options.\\
The Bowtie 2 tool \cite{langmead_fast_2012} was used to query the consensus sequence of each alfalfa tag pair containing a SNP against the \emph{M. truncatula} reference genome Version 4.0 using the \emph{-verysensitivelocal} preset. The BWA alignment tool \cite{li2009fast} was used to align rice tags on Rice Genome Annotation Project Release 7.
